---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dblp

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![R-CMD-check](https://github.com/KTH-Library/dblp/workflows/R-CMD-check/badge.svg)](https://github.com/KTH-Library/dblp/actions)
<!-- badges: end -->

The dblp computer science bibliography at [dblp.org](https://dblp.org) provides open bibliographic information on major computer science journals and proceedings. Originally created at the University of Trier in 1993, dblp is now operated and further developed by Schloss
Dagstuhl. This R package interfaces with the API, making data available to use from R.

## Installation

You can install the development version of dblp from GitHub with:

``` r
#install.packages("devtools")
install_github("KTH-Library/dblp", dependencies = TRUE)
```

## Example

This is a basic example which shows you how make a search :

```{r example}
library(dblp)
library(knitr)
library(stringr)
suppressPackageStartupMessages(library(dplyr))

# search for publications

dblp_search("quantum computer")$content %>%
  select(starts_with("info")) %>%
  mutate(result = paste(`info.title`, `info.ee`, `info.url`)) %>%
  select(result) %>%
  slice(1:5) %>%
  kable()

# crawl when there are many pages of results


search <- dblp_crawl("Royal Institute")$content

# display results
search %>%
  filter(str_detect(`info.ee`, "kth:diva")) %>%
  arrange(desc(`info.year`)) %>%
  # rename and order some named and indexed columns
  select(DOI = `info.doi`, 9:4) %>%
  # add a HTML link by combining title and use DOI for href
  mutate(link = sprintf("<a href='https://doi.org/%s'>%s...</a>", 
    DOI, str_sub(`info.title`, 1, 50))) %>%
  # pick out a few columns to display in a HTML table
  select(link, 1:4, -c("DOI", "info.ee"), `info.year`) %>%
  slice(1:5) %>%
  kable()

# search for venues

dblp_crawl("Europe", entity = "venues")$content %>%
  slice(1:5) %>%
  select(starts_with("info")) %>%
  kable()

# search for authors

dblp_crawl("maguire", entity = "authors")$content %>%
  select(starts_with("info")) %>%
  filter(stringr::str_starts(`info.author`, "Ger")) %>%
  kable()

```

