---
title: "dblp"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{dblp}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The dblp computer science bibliography at [dblp.org](https://dblp.org) provides open bibliographic information on major computer science journals and proceedings. Originally created at the University of Trier in 1993, dblp is now operated and further developed by Schloss
Dagstuhl. This R package interfaces with the API, making data available to use from R.

## Installation

You can install the development version of dblp from GitHub with:

``` r
#install.packages("devtools")
install_github("KTH-Library/dblp", dependencies = TRUE)
```

## Example

This is a basic example which shows you how make a search :

```{r example}
library(dblp)
library(knitr)
library(stringr)
suppressPackageStartupMessages(library(dplyr))

# the live dblp API is occasionally unreachable or rate-limited (this
# happens especially from shared CI runner IPs), so calls below are
# wrapped to degrade gracefully instead of failing the vignette build
safe_content <- function(expr) tryCatch(expr, error = function(e) NULL)

# search for publications

qc <- safe_content(dblp_search("quantum computer")$content)

if (!is.null(qc)) {
  qc %>%
    select(starts_with("info")) %>%
    mutate(result = paste(`info.title`, `info.ee`, `info.url`)) %>%
    select(result) %>%
    slice(1:5) %>%
    kable()
} else {
  cat("_dblp API unavailable at vignette build time; example output omitted._")
}

# crawl when there are many pages of results

search <- safe_content(dblp_crawl("Royal Institute")$content)

# the dblp API omits the info.doi column entirely when none of the
# returned records have a DOI, so ensure it exists before selecting it
if (!is.null(search) && !"info.doi" %in% names(search)) search$info.doi <- NA_character_

# display results
if (!is.null(search)) {
  search %>%
    filter(str_detect(`info.ee`, "kth:diva")) %>%
    arrange(desc(`info.year`)) %>%
    # rename and order some named and indexed columns
    select(DOI = `info.doi`, 9:4) %>%
    # add a HTML link by combining title and use DOI for href
    mutate(link = sprintf("<a href='https://doi.org/%s'>%s...</a>",
      DOI, str_sub(`info.title`, 1, 50))) %>%
    # pick out a few columns to display in a HTML table
    select(link, 1:4, -c("DOI", "info.ee"), `info.year`) %>%
    slice(1:5) %>%
    kable()
} else {
  cat("_dblp API unavailable at vignette build time; example output omitted._")
}

# search for venues

venues <- safe_content(dblp_crawl("Europe", entity = "venues")$content)

if (!is.null(venues)) {
  venues %>%
    slice(1:5) %>%
    select(starts_with("info")) %>%
    kable()
} else {
  cat("_dblp API unavailable at vignette build time; example output omitted._")
}

# search for authors

authors <- safe_content(dblp_crawl("maguire", entity = "authors")$content)

if (!is.null(authors)) {
  authors %>%
    select(starts_with("info")) %>%
    filter(stringr::str_starts(`info.author`, "Ger")) %>%
    kable()
} else {
  cat("_dblp API unavailable at vignette build time; example output omitted._")
}

```

# Altmetric data for specific publication

How to retrieve Altmetric Count for a specific article using the Altmetric from the
Altmetric Details Page - Counts Only API:

```{r}

library(dblp)
library(dplyr)
library(knitr)
library(httr)

# the dblp/Altmetric APIs are occasionally unreachable or rate-limited
# (this happens especially from shared CI runner IPs), so this example
# is wrapped to degrade gracefully instead of failing the vignette build
link <- tryCatch({

  # DOIs found for a specific author
  dois <-
    dblp_search("Gerald Q. Maguire Jr.")$content %>% pull(`info.doi`)

  # Pick one and retrieve Altmetric data from the
  # Altmetric Details Page - Counts Only API
  # https://docs.google.com/spreadsheets/d/1ndVY8Q2LOaZO_P_HDmSQulagjeUrS250mAL2N5V8GvY/edit#gid=0
  # https://help.altmetric.com/support/solutions/articles/6000086844-sample-api-response

  urls <- sprintf("https://api.altmetric.com/v1/doi/%s", dois)
  resp <- GET(urls[6])
  parsed <- content(resp)

  sprintf("<a href='%s' title='%s'><img src='%s'></img>%s with DOI: %s</a>",
    parsed$details_url, parsed$title, parsed$images$medium, parsed$title, parsed$doi)

}, error = function(e) "<em>dblp/Altmetric API unavailable at vignette build time; example output omitted.</em>")

```

We can now display a link to the Altmetric Details Page for this article:

```{r, results="asis",echo=FALSE}

cat(link)

```

Attribution for the above link:

> Altmetrics data is provided by Altmetric.com, a research metrics company who track and collect the online conversations around millions of scholarly outputs. Altmetric continually monitors a variety of non-traditional sources to provide real-time updates on new mentions and shares of individual research outputs, which are collated and presented to users via the Altmetric details pages and badge visualisations. Each research output that Altmetric finds attention for is also given a score; a weighted count of the online attention it has received. Further information about [how the Altmetric Attention Score is calculated is available here](https://www.altmetric.com/about-our-data/the-donut-and-score/).
